\chapter{Experiments}
\label{chap:methodology}
\label{chap:experiments}

\section{Overarching Methodology}
Several of the following sections are about selecting a CA problem and letting CA-NEAT have a go at solving it.
In these experiments, the same basic configuration of CA-NEAT is used.
The size of the CA neighborhood (equal to the number of CPPN inputs) and the number of cell-states (equal to the number of CPPN outputs) is changed to be appropriate to the problem at hand.
The fitness evaluation function is also custom to every problem.

Otherwise the CA-NEAT parameters are the same across different experiments.
These are listed in Appendix TODO.
%Notably, the mutation weigths are biased towards adding nodes and connections moreso than removing them, leading to the average network size growing over time.

Each experiment consists of 100 independent runs with the same parameters but different initial populations.
All experiments have a population size of 200 individuals and elitism degree of 1.
Each generation-population is segregated into species by NEAT, with selection and reproduction happening within these groups.
\textit{Sigma scaled selection} \cite{hancock-1994} is used to select pairs for reproduction.

During development of the system, a variation of different configurations were tried for different problems.
When deciding on the experiments to collect results from for this paper,
a deliberate choice was made to use the same CPPN-NEAT configuration and as close to the same CA configuration as possible for all problems.
This makes it easier to make comparison between experiments, but means that the settings chosen may favor some experiments over others.

\input{experiments/previous_work}
\input{experiments/morphXY}
\input{experiments/majority}
\input{experiments/synchronization}
%\input{experiments/fss}
\input{experiments/properties}
\input{experiments/novelty}
